Reproducibility of COVID-19 pre-prints in 2020

### 2021-06-09 outputs/paper/paper.Rmd
Updates to paper and socarxiv scripts

```{r loadpackages, include=FALSE}
library(here)
library(knitr)
library(lubridate)
library(tidyverse)
library(stargazer)
library(wesanderson)
```

@@

@@

We then checked these pre-prints for open data and code markers using the ODDPub algorithm. This required downloading each pre-print as a PDF and then converting the PDFs to text files. We then conducted the open data and open code detection procedure. This involved searching for keywords and other markers of open data and open code such as references to GitHub repositories and similar. A full listing of these markers is included in Appendix \@ref(markers). This was conducted using the `open_data_search()` function from the `oddpub` package.

@@

all <- rbind(just_arxiv, just_medRxiv, just_bioRxiv)

all %>% 
  mutate(month = floor_date(date, "month")) %>% 
  filter(year(date) >= 2020) %>% 
  ggplot(aes(x = month)) + 
  geom_histogram(aes(fill = type), stat="count", position = "dodge") + 
  labs(title = "Pre-prints posted per month",
       subtitle = "Total of 3,379 relevant pre-prints on arXiv, 3,031 on bioRxiv, 9,929 on medRxiv",
       x = "Month",
       y = "Number of pre-prints",
       fill = "Repository") +
  theme_minimal() +
  scale_fill_manual(values = wes_palette("Darjeeling1"))
```

@@

```{r summarycounts-medRxiv}
# open data/open code count summary table
med_open_data_results %>% 
  count(is_open_data, is_open_code) %>%
  mutate(prop_total = n / sum(n)) %>%
  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>% 
  kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
        caption = "Counts and proportions of open data and code markers in medRxiv sample",
        booktabs = TRUE,
        digits = 2)
```

```{r summarycounts-bioRxiv}
# open data/open code count summary table
bio_open_data_results %>% 
  count(is_open_data, is_open_code) %>%
  mutate(prop_total = n / sum(n)) %>%
  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>% 
  kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
        caption = "Counts and proportions of open data and code markers in bioRxiv sample",
        booktabs = TRUE,
        digits = 2)
```

@@

```{r monthly-papers-condition-stack, fig.cap = "Number of pre-prints related to COVID-19 sampled from medRxiv, distinguished by presence of open data or code markers", out.width="90%", fig.align = "center"}
# Number of papers for each open data/code status per month
open_status <- 
  med_open_data_results %>% 
  select(title, date, is_open_code, is_open_data) %>% 
  mutate(condition = is_open_data + is_open_code)
open_status$condition[open_status$condition == 2] <- "Both"
open_status$condition[open_status$condition == 0] <- "Neither"
open_status$condition[open_status$condition == 1 & open_status$is_open_code == 1] <- "Open Code"
open_status$condition[open_status$condition == 1 & open_status$is_open_data == 1] <- "Open Data"

open_status %>% 
  ggplot() + 
  geom_bar(aes(x = factor(floor_date(date, "month")), 
               fill=factor(condition, levels = c("Neither", "Open Code", "Open Data", "Both")), 
               position = "stack")) +
  labs(fill = "Type of marker") +
  scale_x_discrete(breaks=c("2020-01-01","2020-04-01","2020-07-01", "2020-10-01", "2021-01-01"), 
                   labels=c("Jan 2020","Apr 2020","Jul 2020", "Oct 2020", "Jan 2021")) +
  ylab("Number of pre-prints") +
  xlab("Month") +
  labs(title="Sampled pre-prints by month", subtitle="medRxiv, Total = 1,200") +
  theme_minimal()
```

```{r monthly-proportion-of-open, fig.cap= "Proportion of pre-prints in sample with open data or open code markers by month", out.width="90%", fig.align = "center"}
# Proportion of papers posted with open data or open code each month
colors <- c("Open Data" = "blue", "Open Code" = "green")
med_month_sum_cov <- 
  med_open_data_results %>% 
  group_by(month = floor_date(date, "month")) %>% 
  summarise(count=n(), prop_open_code = sum(is_open_code)/n(), prop_open_data = sum(is_open_data)/n()) %>% 
  mutate(num_days = days_in_month(month),
         daily_rate = count/num_days)
med_month_sum_cov %>%
  ggplot() +
  geom_line(data = med_month_sum_cov, aes(month, prop_open_data, color = "Open data")) +
  geom_line(data = med_month_sum_cov, aes(month, prop_open_code, color = "Open code")) +
  ggtitle("Proportion of sampled pre-prints with open data or code markers") +
  labs(colour = "Type of marker",
       x = "Month",
       y = "Proportion of pre-prints") + 
  theme_minimal()
```

@@

```{r open-published-summary}
published_open_status <- 
  med_open_data_results %>% 
  select(title, date, published, is_open_code, is_open_data) %>% 
  mutate(condition = is_open_data + is_open_code)
published_open_status$condition[published_open_status$condition == 2] <- "Both"
published_open_status$condition[published_open_status$condition == 0] <- "Neither"
published_open_status$condition[published_open_status$condition == 1 & published_open_status$is_open_code == 1] <- "Open code"
published_open_status$condition[published_open_status$condition == 1 & published_open_status$is_open_data == 1] <- "Open data"

published_open_status %>% 
  count(published, condition) %>% 
  pivot_wider(names_from = condition, values_from = n) %>%
  mutate(published = ifelse(published == 0, "No", "Yes"), `Proportion with either/both`= round((`Open data` + `Open code` + Both)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
  rename(Published = published) %>%
  kable(caption = "Counts and proportions of open data markers by whether the pre-print was published",
        booktabs = TRUE)
```

@@

published_open_status %>% 
  # mutate(published = ifelse(published == 0, "Unpublished", "Published")) +
  ggplot() + 
  geom_bar(aes(x = published, fill=factor(condition, levels = c("Neither", "Open code", "Open data", "Both")), position = "stack")) +
  labs(fill = "Type of marker",
       y = "Number of pre-prints",
       x = "Publication status") +
  ggtitle("Pre-prints by publication status") +
  theme_minimal()
```

@@

# Number of open data/code papers by keyword for different types
paper_type_keywords <- 
  med_open_data_results %>% select(title, abstract, date, is_open_code, is_open_data) %>% 
  mutate(condition = is_open_data + is_open_code)
paper_type_keywords$condition[paper_type_keywords$condition == 2] <- "Both"
paper_type_keywords$condition[paper_type_keywords$condition == 0] <- "Neither"
paper_type_keywords$condition[paper_type_keywords$condition == 1 & open_status$is_open_code == 1] <- "Open code"
paper_type_keywords$condition[paper_type_keywords$condition == 1 & open_status$is_open_data == 1] <- "Open data"
paper_type_keywords$`Machine Learning` <- str_detect( paper_type_keywords$title, "machine learning") | 
                                          str_detect( paper_type_keywords$abstract, "machine learning")
paper_type_keywords$Simulation <- str_detect( paper_type_keywords$title, "simulate|simulation|simulating") | 
                                    str_detect( paper_type_keywords$abstract, "simulate|simulation|simulating|simulated")
paper_type_keywords$modelling <- str_detect( paper_type_keywords$title, "modelling|model|models|modeling") | 
                                str_detect( paper_type_keywords$abstract, "modelling|model|models|modeling")
paper_type_keywords <- paper_type_keywords %>% 
  pivot_longer(cols = c("Machine Learning", "Simulation", "modelling"), names_to = "Type", values_to = "Value") %>%
  filter(Value == TRUE)

# # Plot
# paper_type_keywords %>% ggplot() + 
#   geom_bar(aes(x = Type, fill=factor(condition, levels = c("Neither", "Open code", "Open data", "Both")), position = "stack")) +
#   labs(fill = "Type of marker") +
#   scale_x_discrete(labels=c("Machine learning", "Modelling", "Simulation")) +
#   ylab("Number of pre-prints") +
#   xlab("Month") +
#   ggtitle("Sampled pre-prints by type") +
#   theme_minimal()
```

```{r summary-by-type}
paper_type_keywords %>% 
  count(Type, condition) %>% 
  pivot_wider(names_from = condition, values_from = n, values_fill = 0) %>% 
  mutate(Type = if_else(Type == "modelling", "Modelling", Type),
         Type = if_else(Type == "Machine Learning", "Machine learning", Type),
         ) %>% 
  mutate(`Proportion with either/both`= round((`Open data` + `Open code` + Both)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
  kable(caption = "Counts and proportions of open data markers by the type of pre-print",
        booktabs = TRUE)
```

@@

Open data is generally accepted to be beneficial to the scientific process, and to a paper's reproducibility potential, hence it is concerning that over 80 per cent of pre-prints in our sample contained no open data markers. This concern is slightly mitigated by recognition of challenges in working with biomedical data compared with data in other fields, notably privacy and ethics concerns when working with personal data [@Floca2014]. The COVID-19 pandemic has seen an uptake in open science practices globally, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University [@citeCSSE] or the large number of publishers who have removed paywalls from published COVID-19 research [@gill2020]. An important next step may compare open data and code availability in COVID-19 pre-prints with those from other topics posted to medRxiv to examine whether the pandemic has increased transparency from the previous norm.

Open code as an open science marker is much more context and field-dependent, as not all biomedical research papers will rely on computational methods for their analyses. However, in pre-prints where code comprises a large portion of the methodology or results, posting it openly to repositories like GitHub contributes greatly to a pre-print's potential reproducibility. This gains importance as computational methods become increasingly popular in the rush to form predictions about emerging situations with limited data or laboratory research, which was the case for modelling studies in the early days of the COVID-19 pandemic (CITE). We also see growing concern over the quality and consequences of this sort of research, with bioRxiv not allowing purely computational work [@kwon2020].

>>>>

```{r loadpackages, include=FALSE}
library(here)
library(knitr)
library(lubridate)
library(tidyverse)
library(stargazer)
library(wesanderson)
library(kableExtra)
```

@@

socarxiv_open_data_results <- 
  read_csv(here::here("outputs/data/socarxiv_open_data_results.csv"))
socarxiv_results <- 
  read_csv(here::here("outputs/data/socarxiv_results.csv")) # All COVID medRxiv papers (9,929)

@@

We then checked these pre-prints for open data and code markers using the ODDPub algorithm. This required downloading each pre-print as a PDF and then converting the PDFs to text files. Some papers from SocArxiv were only available in .docx format and were downloaded as such instead. We then conducted the open data and open code detection procedure. This involved searching for keywords and other markers of open data and open code such as references to GitHub repositories and similar. A full listing of these markers is included in Appendix \@ref(markers). This was conducted using the `open_data_search()` function from the `oddpub` package.

@@

just_socarxiv <- 
  socarxiv_results  %>% 
  select(date_created) %>%
  rename(date = "date_created") %>%
  mutate(type = "socArXiv")

all <- rbind(just_arxiv, just_medRxiv, just_bioRxiv, just_socarxiv)

all %>% 
  mutate(month = floor_date(date, "month")) %>% 
  filter(year(date) >= 2020) %>% 
  ggplot(aes(x = month)) + 
  geom_histogram(aes(fill = type), stat="count", position = "dodge") + 
  labs(title = "COVID-19-related pre-prints posted per month",
       subtitle = "Total of 3,812 relevant pre-prints on arXiv, 3,714 on bioRxiv, 12,060 on medRxiv, 444 on socArXiv",
       x = "Month",
       y = "Number of pre-prints",
       fill = "Repository") +
  theme_minimal() +
  scale_fill_manual(values = wes_palette("Darjeeling1"))
```

@@

```{r summarycounts-medRxiv, }
# open data/open code count summary table

just_arxiv <-
  arxiv_open_data_results  %>%
  select(submitted, is_open_data, is_open_code) %>%
  mutate(type = "arXiv") %>%
  rename(date = submitted)

just_medRxiv <-
  med_open_data_results  %>%
  select(date, is_open_data, is_open_code) %>%
  mutate(type = "medRxiv")

just_bioRxiv <-
  bio_open_data_results  %>%
  select(date, is_open_data, is_open_code) %>%
  mutate(type = "bioRxiv")

just_socarxiv <-
  socarxiv_open_data_results  %>%
  select(date_created, is_open_data, is_open_code) %>%
  rename(date = "date_created") %>%
  mutate(type = "socArXiv")

all <- rbind(just_arxiv, just_medRxiv, just_bioRxiv, just_socarxiv)

all %>%
  group_by(type) %>%
  count(is_open_data, is_open_code) %>%
  mutate(prop_total = n / sum(n)) %>%
  mutate(is_open_data = ifelse(is_open_data == 0, "No", "Yes"),
         is_open_code = ifelse(is_open_code == 0, "No", "Yes")) %>%
  ungroup() %>%
  select(is_open_data, is_open_code, n, prop_total) %>%
  kable(col.names = c("Open data markers", "Open code markers", "Count", "Proportion of total"),
        caption = "Counts and proportions of open data and code markers in medRxiv sample",
        booktabs = TRUE,
        digits = 2) %>%
  group_rows(index = c("arXiv" = 4, "bioRxiv" = 4, "medRxiv" = 4, "socArXiv" = 4))
```

@@

```{r monthly-papers-condition-stack, fig.cap = "Number of pre-prints related to COVID-19 sampled from medRxiv, distinguished by presence of open data or code markers", out.width="90%", fig.align = "center"}
# Number of papers for each open data/code status per month
open_status_med <- 
  med_open_data_results %>% 
  select(title, date, is_open_code, is_open_data) %>% 
  mutate(condition = is_open_data + is_open_code, repo = "medRxiv")

open_status_bio <- 
  bio_open_data_results %>% 
  select(title, date, is_open_code, is_open_data) %>% 
  mutate(condition = is_open_data + is_open_code, repo = "bioRxiv")

open_status_arxiv <- 
  arxiv_open_data_results %>% 
  select(title, submitted, is_open_code, is_open_data) %>% 
  mutate(condition = is_open_data + is_open_code, repo = "arXiv") %>%
  rename(date = submitted)

open_status_socarxiv <- 
  socarxiv_open_data_results %>% 
  select(title, date_created, is_open_code, is_open_data) %>% 
  mutate(condition = is_open_data + is_open_code, repo = "socArXiv") %>%
  rename(date = date_created)

open_status <- rbind(open_status_med, open_status_bio, open_status_arxiv, open_status_socarxiv)

open_status$condition[open_status$condition == 2] <- "Both"
open_status$condition[open_status$condition == 0] <- "Neither"
open_status$condition[open_status$condition == 1 & open_status$is_open_code == 1] <- "Open Code"
open_status$condition[open_status$condition == 1 & open_status$is_open_data == 1] <- "Open Data"

open_status %>% 
  ggplot() + 
  geom_bar(aes(x = factor(floor_date(date, "month")), 
               fill=factor(condition, levels = c("Neither", "Open Code", "Open Data", "Both")), 
               position = "stack")) +
  labs(fill = "Type of marker") +
  scale_x_discrete(breaks=c("2020-01-01","2020-07-01", "2021-01-01"), 
                   labels=c("Jan 2020", "Jul 2020", "Jan 2021")) +
  ylab("Number of pre-prints") +
  xlab("Month") +
  labs(title="Sampled pre-prints by month", subtitle="medRxiv, Total = 1,200") +
  theme_minimal() +
  scale_fill_manual(values = wes_palette("Darjeeling1")) +
  facet_wrap(~repo)
```

```{r monthly-proportion-of-open, fig.cap= "Proportion of pre-prints in sample with open data or open code markers by month", out.width="90%", fig.align = "center"}
# Proportion of papers posted with open data or open code each month
med_month_sum_cov <- 
  med_open_data_results %>% 
  group_by(month = floor_date(date, "month")) %>% 
  summarise(count = n(), "Open Code" = mean(is_open_code), "Open Data" = mean(is_open_data)) %>% 
  mutate(daily_rate = count/days_in_month(month), repo = "medRxiv")

bio_month_sum_cov <- 
  bio_open_data_results %>% 
  group_by(month = floor_date(date, "month")) %>% 
  summarise(count = n(), "Open Code" = mean(is_open_code), "Open Data" = mean(is_open_data)) %>% 
  mutate(daily_rate = count/days_in_month(month), repo = "bioRxiv")

arxiv_month_sum_cov <- 
  arxiv_open_data_results %>% 
  group_by(month = floor_date(submitted, "month")) %>% 
  summarise(count = n(), "Open Code" = mean(is_open_code), "Open Data" = mean(is_open_data)) %>% 
  mutate(daily_rate = count/days_in_month(month), repo = "arXiv")

socarxiv_month_sum_cov <- 
  socarxiv_open_data_results %>% 
  group_by(month = floor_date(date_created, "month")) %>% 
  summarise(count = n(), "Open Code" = mean(is_open_code), "Open Data" = mean(is_open_data)) %>% 
  mutate(daily_rate = count/days_in_month(month), repo = "socArXiv")

month_sum_cov <- rbind(med_month_sum_cov, bio_month_sum_cov, arxiv_month_sum_cov, socarxiv_month_sum_cov) %>%
  pivot_longer(cols = c("Open Data", "Open Code")) %>%
  filter(value != 1) # Removes outliers where small number of papers in a month was sampled and both had open data/code

# TODO: Fix date labels, facet_wrap labels
month_sum_cov %>%
  ggplot() +
  geom_line(data = month_sum_cov, aes(month, value, color = repo)) +
  ggtitle("Proportion of sampled pre-prints with open data or code markers") +
  labs(colour = "Repository",
       x = "Month",
       y = "Proportion of pre-prints") + 
  theme_minimal() +
  scale_color_manual(values = wes_palette("Darjeeling1")) +
  facet_wrap(~name)

```

@@

```{r open-published-summary}
# Maybe find a way to use the data frames constructed above instead of constructing new ones?
med_published_open_status <- 
  med_open_data_results %>% 
  select(title, date, published, is_open_code, is_open_data) %>% 
  mutate(condition = is_open_data + is_open_code, repo = "medRxiv")

bio_published_open_status <- 
  bio_open_data_results %>% 
  select(title, date, published, is_open_code, is_open_data) %>% 
  mutate(condition = is_open_data + is_open_code, repo = "bioRxiv")

published_open_status <- rbind(med_published_open_status, bio_published_open_status)

published_open_status$condition[published_open_status$condition == 2] <- "Both"
published_open_status$condition[published_open_status$condition == 0] <- "Neither"
published_open_status$condition[published_open_status$condition == 1 & published_open_status$is_open_code == 1] <- "Open code"
published_open_status$condition[published_open_status$condition == 1 & published_open_status$is_open_data == 1] <- "Open data"

published_open_status %>%
  count(repo, published, condition) %>% 
  pivot_wider(names_from = condition, values_from = n) %>%
  mutate(Published = ifelse(published == 0, "No", "Yes"), `Proportion with either/both`= round((`Open data` + `Open code` + Both)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
  select(Published, Both, Neither, `Open code`, `Open data`, `Proportion with either/both`) %>%
  kable(caption = "Counts and proportions of open data markers by whether the pre-print was published",
        booktabs = TRUE) %>%
  group_rows(index = c("bioRxiv" = 2, "medRxiv" = 2))
```

@@

published_open_status %>% 
  mutate(published = ifelse(published == 0, "Unpublished", "Published")) %>%
  ggplot() + 
  geom_bar(aes(x = published, fill=factor(condition, levels = c("Neither", "Open code", "Open data", "Both")), position = "stack")) +
  labs(fill = "Type of marker",
       y = "Number of pre-prints",
       x = "Publication status") +
  ggtitle("Pre-prints by publication status") +
  theme_minimal() +
  facet_wrap(~repo) + 
  scale_fill_manual(values = wes_palette("Darjeeling1"))

```

@@

# Number of open data/code papers by keyword for different types
med_paper_type_keywords <- 
  med_open_data_results %>% select(title, abstract, date, is_open_code, is_open_data) %>% 
  mutate(condition = is_open_data + is_open_code, repo = "medRxiv")

bio_paper_type_keywords <- 
  bio_open_data_results %>% select(title, abstract, date, is_open_code, is_open_data) %>% 
  mutate(condition = is_open_data + is_open_code, repo = "bioRxiv")

arxiv_paper_type_keywords <- 
  arxiv_open_data_results %>% select(title, abstract, submitted, is_open_code, is_open_data) %>% 
  rename(date = submitted) %>%
  mutate(condition = is_open_data + is_open_code, repo = "arXiv")

socarxiv_paper_type_keywords <- 
  socarxiv_open_data_results %>% select(title, description, date_created, is_open_code, is_open_data) %>% 
  rename(date = date_created, abstract = description) %>%
  mutate(condition = is_open_data + is_open_code, repo = "socArXiv")

paper_type_keywords <- rbind(med_paper_type_keywords, bio_paper_type_keywords, arxiv_paper_type_keywords, socarxiv_paper_type_keywords)

paper_type_keywords$condition[paper_type_keywords$condition == 2] <- "Both"
paper_type_keywords$condition[paper_type_keywords$condition == 0] <- "Neither"
paper_type_keywords$condition[paper_type_keywords$condition == 1 & paper_type_keywords$is_open_code == 1] <- "Open code"
paper_type_keywords$condition[paper_type_keywords$condition == 1 & paper_type_keywords$is_open_data == 1] <- "Open data"

paper_type_keywords$`Machine Learning` <- str_detect( paper_type_keywords$title, "machine learning") | 
                                          str_detect( paper_type_keywords$abstract, "machine learning")
paper_type_keywords$Simulation <- str_detect( paper_type_keywords$title, "simulate|simulation|simulating") | 
                                    str_detect( paper_type_keywords$abstract, "simulate|simulation|simulating|simulated")
paper_type_keywords$modelling <- str_detect( paper_type_keywords$title, "modelling|model|models|modeling") | 
                                str_detect( paper_type_keywords$abstract, "modelling|model|models|modeling")
paper_type_keywords <- paper_type_keywords %>% 
  pivot_longer(cols = c("Machine Learning", "Simulation", "modelling"), names_to = "Type", values_to = "Value") %>%
  filter(Value == TRUE)

# # Plot
paper_type_keywords %>% ggplot() +
  geom_bar(aes(x = Type, fill=factor(condition, levels = c("Neither", "Open code", "Open data", "Both")), position = "stack")) +
  labs(fill = "Type of marker") +
  scale_x_discrete(labels=c("Machine learning", "Modelling", "Simulation")) +
  ylab("Number of pre-prints") +
  xlab("Month") +
  ggtitle("Sampled pre-prints by type") +
  theme_minimal() +
  scale_fill_manual(values = wes_palette("Darjeeling1")) +
  facet_wrap(~repo)

```

```{r summary-by-type}
paper_type_keywords %>% 
  count(repo, Type, condition) %>% 
  pivot_wider(names_from = condition, values_from = n, values_fill = 0) %>% 
  mutate(Type = if_else(Type == "modelling", "Modelling", Type),
         Type = if_else(Type == "Machine Learning", "Machine learning", Type),
         ) %>% 
  mutate(`Proportion with either/both`= round((`Open data` + `Open code` + Both)/(`Open data` + `Open code` + Both + Neither), 2)) %>%
  select(!repo) %>%
  kable(caption = "Counts and proportions of open data markers by the type of pre-print",
        booktabs = TRUE) %>%
  group_rows(index = c("arxiv" = 3, "bioRxiv" = 3, "medRxiv" = 3, "socArXiv" = 3))
```

@@

Open data is generally accepted to be beneficial to the scientific process, and to a paper's reproducibility potential, hence it is concerning that over 80 per cent of pre-prints in our sample contained no open data markers. This concern is slightly mitigated by recognition of challenges in working with biomedical data compared with data in other fields, notably privacy and ethics concerns when working with personal data [@Floca2014]. The COVID-19 pandemic has seen an uptake in open science practices globally, as evidenced by the creation of open data repositories such as the dashboard maintained by the Center for Systems Science and Engineering at Johns Hopkins University [@citeCSSE] or the large number of publishers who have removed paywalls from published COVID-19 research [@gill2020]. (MENTION/REFERENCE https://wellcome.org/coronavirus-covid-19/open-data ?) An important next step may compare open data and code availability in COVID-19 pre-prints with those from other topics posted to medRxiv to examine whether the pandemic has increased transparency from the previous norm.

Open code as an open science marker is much more context and field-dependent, as not all biomedical research papers will rely on computational methods for their analyses. However, in pre-prints where code comprises a large portion of the methodology or results, posting it openly to repositories like GitHub contributes greatly to a pre-print's potential reproducibility. This gains importance as computational methods become increasingly popular in the rush to form predictions about emerging situations with limited data or laboratory research, which was the case for modelling studies in the early days of the COVID-19 pandemic (CITE). We also see growing concern over the quality and consequences of this sort of research, with bioRxiv no longer allowing purely computational work [@kwon2020].
